R für die sozio-ökonomische Forschung

### 2020-09-06 Chap-visualization.Rmd
Icae Design taken out

```{r, warning=FALSE, message=FALSE}
library(here)
library(tidyverse)
library(icaeDesign)
library(data.table)
library(ggpubr)
library(ggrepel)
library(scales)
library(tufte)
library(gapminder)
library(viridis)
library(latex2exp)
library(WDI)
library(countrycode)
```

>>>>

```{r, warning=FALSE, message=FALSE}
library(here)
library(tidyverse)
library(data.table)
library(ggpubr)
library(ggrepel)
library(scales)
library(tufte)
library(gapminder)
library(viridis)
library(latex2exp)
library(WDI)
library(countrycode)
```
